\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    #1 \vspace{-2pt}
  }
}

\newcommand{\techStack}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeCertificates}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & #2
    \end{tabular*}\vspace{-1pt}
}

\newcommand{\resumeSubheadingContinue}[2]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingTechStack}[1]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small#1}
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  DOCUMENT STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://nandaja.me/}{\huge Nandaja Yarramareddy}} & Email : \href{mailto:yarramareddynandaja@gmail.com}{yarramareddynandaja@gmail.com}\\
  \href{https://nandaja.me/}{\textit{https://nandaja.me}} & Mobile : +91-8919544901 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {INFOSYS LIMITED}{Hyderabad, India}
      {Senior Systems Engineer}{}
      \resumeItemListStart
        \resumeItem 
          {2.5 years of experience in the development of responsive web applications for Retail and Energy domains.}
        \resumeItem 
          {Developed, enhanced, and migrated multiple web-based applications on the .NET framework with technical expertise in ASP.NET MVC, Angular4, React JS, Web API, Oracle, Microsoft SQL Server, and JavaScript.}
      \resumeItemListEnd
        
    % \resumeSubheadingContinue
    \resumeItemListStart
        \resumeItem{Gas leak Survey System (GLSS)}
      \resumeItemListStart
        \techStack{Technologies}{Angular4, ASP.NET, Web API, C\#, Oracle, SSIS, Bootstrap, JQuery.}
        \resumeItem
          {GLSS is a web application used by Southern Company Gas for surveillance and maintenance of gas delivery systems across multiple states in the USA.}
        \resumeItem
          {Developed a responsive UI, implemented packages and stored procedures for data retrieval and updating data, Web APIs for business logic.}
        \resumeItem
          {Implemented the testing suite including the Unit tests and Integration tests and delivered within the specified timelines.}
        \resumeItem
          {Deployed in all environments, and provided support during and after deployment.}
      \resumeItemListEnd
    \resumeItemListEnd
    \resumeItemListStart
        \resumeItem{Win2K3 Project}
      \resumeItemListStart
        \techStack{Technologies}{ASP.NET, JQuery and HTML.}
        \resumeItem
          {The purpose of the Win2K3 project was to migrate Windows server applications to a newer version.}
        \resumeItem
          {Migrated various applications to Windows Server 2012 from Windows server 2003.}
        \resumeItem
          {Involved in migrating the Framework related changes from .NET 3.5 to .NET 4.5.1.}
        \resumeItem
          {Worked on the web applications to make them compatible with latest versions of all browsers.}
      \resumeItemListEnd
    \resumeItemListEnd
    \resumeItemListStart
        \resumeItem{Microsoft Excel Automation}
      \resumeItemListStart
        \techStack{Technologies}{ADO.NET}
        \resumeItem
          {The purpose of this automation was to reduce a significant time of company resources working on Microsoft Excel sheets.}
        \resumeItem
          {Created an Automation Application for Microsoft Excel by using Microsoft C\# .NET.}
        \resumeItem
          {This application is used to merge and modify Excel workbooks automatically in real-time.}
      \resumeItemListEnd
    \resumeItemListEnd
    \resumeSubheading
      {L.G POLYMERS INDIA Pvt. Ltd.,}{Vishakapatnam, India}
      {Intern}{May 2015}
      \resumeItemListStart
        \resumeItem
          {Observed different operations performed in the manufacture of polystyrene.}
        \resumeItem
          {Designed Shell and tube heat exchanger for a specified flow conditions }
       
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Sri Venkateswara University college of Engineering}{Tirupati, India}
    {Bachelor of Technology in Chemical Engineering;  GPA: 7.2/10}{Sept 2012 -- May 2016}
\resumeSubHeadingListEnd


% % --------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
  \techStack
    {Languages} { C\#, JavaScript, SQL, Python, HTML, CSS, TypeScript}
  \techStack
    {Frameworks} {ReactJS, Bootstrap,ASP.NET Core, MVC, ASP.NET Web API, AngularJS,  Material UI}
  \techStack
    {Databases} { MS SQL Server, Oracle, SSIS}
  \techStack
    {VCS} {Git, MS Team foundation server}
 \resumeSubHeadingListEnd

%-----------Projects-----------------
\section{Projects}
\resumeSubHeadingListStart
  \resumeItem
    {Web Portfolio - \href{https://nandaja.me/}{\textit{https://nandaja.me}}}
    \resumeItemListStart
    \resumeItem
    {Designed and created my web porfolio}
    \resumeItemListEnd
    \resumeItem{Other Projects - \href{https://github.com/ynand}{\textit{https://github.com/ynand}}}
\resumeSubHeadingListEnd
\end{document}