

%-----------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-----------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.40in,top=0.3in,right=0.75in,bottom=0.1in]{geometry} 
\usepackage{fontawesome}
\usepackage{times}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Nandaja Yarramareddy} 

\address{ \href{ https://nandajayarramareddy.github.io}{\faChrome{ https://nandajayarramareddy.github.io}} \faEnvelope{ yarramareddynandaja@gmail.com}}

\begin{document}

%-----------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%-----------------------------------------------------------------

\begin{rSection}{Work Experience}

{\bf Infosys Limited, Hyderabad } %\hfill {\em 2016 - 2018} 
\\{\textit{Full-stack developer}}\\
- 2.5 years of experience in the development of responsive web applications for Retail and Energy domains. 
\\- Development, Enhancement, and Migration of multiple web-based applications on the .NET framework with technical expertise in ASP.NET MVC, Angular4, React JS, Web API, Oracle, Microsoft SQL Server, and JavaScript.  
\\- Coding within the prescribed guidelines and conventions of the project and delivering the functionalities within the timeline following Agile methodology.

% {\bf LG Polymers India Pvt., ltd, }  
% \\{\textit{Intern}}
% \\- Observed different operations performed in the manufacture of polystyrene.
% \\- Studied in detail about the heat exchangers and their performance. Performed calculations on design of Shell and tube heat exchangers at the given conditions on an Excel Sheet.

\end{rSection}
%-----------------------------------------------------------------
%	EDUCATION SECTION
%-----------------------------------------------------------------

\begin{rSection}{Education}

{\bf Sri Venkateswara University college of Engineering, Tirupati } %\hfill {\em 2012 - 2016} 
\\{ \textit {B.Tech in Chemical Engineering  }} 

\end{rSection}
%-----------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%-----------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages: \ & C\#, JavaScript, SQL, Python, HTML, CSS, TypeScript \\
Frameworks: \ & ASP.NET MVC, ASP.NET Web API, AngularJS, Bootstrap, ReactJS, Material UI  \\
Databases: \ & MS SQL Server, Oracle, SSIS \\
VCS: \ & MS Team foundation server, GitHub
\end{tabular}

\end{rSection}

%-----------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------
\begin{rSection}{Projects}
{\bf My Portfolio}
\\{\textit{ Created my portfolio website using ReactJS.}}
\\{\textit{Technologies used:}} ReactJS, Material UI, Github pages

{\bf Gas leak Survey System (GLSS)}
\\{\textit{ GLSS is a web application used by Southern company Gas for surveillance and maintenance of Gas delivery systems across several states in the USA.}}
\\{\textit{Technologies used:}} Angular4, MS.NET 4.6, Web API, C\#, Oracle, SSIS, Bootstrap, JQuery.
\\- Developed responsive UI, implemented packages and stored procedures for data retrieval and updating data, Web APIs for business logic. 
\\- Tested and delivered within the specified timelines.
\\- Automating builds in the server using TFS Build.
\\- Deployed in all environments, and provided support during and after deployment. 

{\bf Win2K3 Project}
\\{\textit{The purpose of the Win2K3 project was to migrate Windows server applications to a newer version.}}
\\{\textit{Technologies used:}} MS.NET 4.5.1, JQuery and HTML
\\- Migrated various applications to Windows Server 2012 from Windows server 2003.
\\- Involved in migrating the Framework related changes from .NET 3.5 to .NET 4.5.1.
\\- Modifying the UI part of applications and Testing the compatibility of migrated applications with both IE11 and Chrome.

{\bf Microsoft Excel Automation}
\\{\textit{The purpose of this automation was to reduce a significant time of company resources working on Microsoft Excel sheets }}
\\{\textit{Technology used:}} ADO.NET
\\- Created an Automation Application for Microsoft Excel by using Microsoft C\# .NET.
\\- This application is used to merge and modify Excel workbooks automatically in real-time.
{\bf }


\end{rSection}


\end{document}